Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-08-29 manuscript.Rmd
Minor updates to figure cross-references in captions.

```{r pupildata, fig.cap="Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Negative values indicate constriction relative to baseline, and positive values indicate dilation. Panel (b) shows the average Fourier spectrum (absolute amplitude values). Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 1). Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", echo=FALSE}

@@

colnames(tabledata) <- c('Data set','Z','k','w','Rmax')
kable(tabledata, align='lcccc',caption = 'Summary of median parameter values.')

@@

```{r methodsfig, fig.cap="Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1. Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels). Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\\% regardless of the target contrast. Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3. The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background). The left and right eye assignments were counterbalanced across trials in the experiment (i.e. the monocular stimulus could be shown to either eye with equal probability).", fig.align="center", echo=FALSE}

@@

```{r appendixfig1, fig.cap="Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.", fig.align="center", echo=FALSE}

@@

```{r appendixfig2, fig.cap="Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 3 for a description of each panel.", fig.align="center", echo=FALSE}

>>>>

```{r pupildata, fig.cap="Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Negative values indicate constriction relative to baseline, and positive values indicate dilation. Panel (b) shows the average Fourier spectrum (absolute amplitude values). Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 8). Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", echo=FALSE}

@@

colnames(tabledata) <- c('Data set','Z','n','w','Rmax')
kable(tabledata, align='lcccc',caption = 'Summary of median parameter values.')

@@

```{r methodsfig, fig.cap="Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1. Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels). Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\\% regardless of the target contrast. Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 1 and 2. The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background). The left and right eye assignments were counterbalanced across trials in the experiment (i.e. the monocular stimulus could be shown to either eye with equal probability).", fig.align="center", echo=FALSE}

@@

```{r appendixfig1, fig.cap="Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 1 for a description of each panel.", fig.align="center", echo=FALSE}

@@

```{r appendixfig2, fig.cap="Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.", fig.align="center", echo=FALSE}

### 2023-08-29 manuscript.tex
Updater authors' inofrmation
Minor updates to figure cross-references in captions.

\title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
\author{Federico G. Segala, Aurelio Bruno, Joel T. Martin,\\
Myat T. Aung, Alex R. Wade \& Daniel H. Baker\\
Department of Psychology, University of York, UK\\
\emph{eLife} (2023) \url{https://doi.org/10.7554/eLife.87048}}
\date{}

@@

@@

@@

\caption{Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1. Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels). Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\% regardless of the target contrast. Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3. The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background). The left and right eye assignments were counterbalanced across trials in the experiment (i.e. the monocular stimulus could be shown to either eye with equal probability).}\label{fig:methodsfig}
\end{figure}

@@

\caption{Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Negative values indicate constriction relative to baseline, and positive values indicate dilation. Panel (b) shows the average Fourier spectrum (absolute amplitude values). Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 1). Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
\end{figure}

\caption{Ratio of binocular to monocular response for three data types. These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f. Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
\end{figure}

\caption{\label{tab:paramtable}Summary of median parameter values.}
\centering
\begin{tabular}[t]{l|c|c|c|c}
\hline
Data set & Z & k & w & Rmax\\
\hline
Pupillometry & 3.44 & 0.01 & 0.61 & 0.00023\\
\hline
EEG 1F & 2.62 & 0.15 & 0.02 & 0.00336\\
\hline
EEG 2F & 3.71 & 0.07 & 0.02 & 0.0031\\
\hline
Matching & 0.30 & 5.10 & 0.09 & -\\
\hline
\end{tabular}
\end{table}

@@

\caption{Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.}\label{fig:appendixfig1}
\end{figure}

@@

\caption{Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 3 for a description of each panel.}\label{fig:appendixfig2}
\end{figure}

>>>>

\title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
\author{Federico G. Segala\(^1\), Aurelio Bruno\(^2\), Joel T. Martin\(^1\), Myat T. Aung\(^1\), Alex R. Wade\(^1\)\\
\& Daniel H. Baker\(^1\)\\
\emph{eLife} (2023) \url{https://doi.org/10.7554/eLife.87048}}
\date{}

@@

\(^1\)Department of Psychology, University of York, York, UK. YO10 5DD\\
\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, UK. LE1 7RH

Address for correspondence: Federico G. Segala, \url{fgs502@york.ac.uk}

@@

\caption{Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Negative values indicate constriction relative to baseline, and positive values indicate dilation. Panel (b) shows the average Fourier spectrum (absolute amplitude values). Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 8). Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
\end{figure}

\caption{Ratio of binocular to monocular response for three data types. These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f. Each value is the average ratio across N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
\end{figure}

\caption{\label{tab:paramtable}Summary of median parameter values.}
\centering
\begin{tabular}[t]{l|c|c|c|c}
\hline
Data set & Z & n & w & Rmax\\
\hline
Pupillometry & 3.44 & 0.01 & 0.61 & 0.00023\\
\hline
EEG 1F & 2.62 & 0.15 & 0.02 & 0.00336\\
\hline
EEG 2F & 3.71 & 0.07 & 0.02 & 0.0031\\
\hline
Matching & 0.30 & 5.10 & 0.09 & -\\
\hline
\end{tabular}
\end{table}

@@

\caption{Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1. Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels). Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\% regardless of the target contrast. Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 1 and 2. The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background). The left and right eye assignments were counterbalanced across trials in the experiment (i.e. the monocular stimulus could be shown to either eye with equal probability).}\label{fig:methodsfig}
\end{figure}

@@

@@

\caption{Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 1 for a description of each panel.}\label{fig:appendixfig1}
\end{figure}

@@

\caption{Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.}\label{fig:appendixfig2}
\end{figure}
